\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-16 manuscript.Rmd
Updates

```{r dependencymanager, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(warning = F, error = F, message = F)
set.seed(123)
par(family = "Helvetica")
```

@@

```{r setup}

@@

Our study had four objectives. First, to develop an instrument to assess an individual's light exposure behavior. Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure. The third one is to gather structural validity evidence for the latent structure obtained in EFA. Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]

@@

```{r Parallel}

@@

```{r ScreePlot}
Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)

@@

```{r Hull}
# HULL
hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ theme(panel.grid.major = element_blank(),
                                               panel.grid.minor = element_blank(),
                                               panel.background = element_blank(),
                                               axis.line.x = element_line(color='black'),
                                               axis.line.y = element_line(color='black'))

@@

```{r}
#MAP
psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
```

>>>>

```{r dependencymanager, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
set.seed(123)
par(family = "Helvetica")
```

@@

```{r setup, include=FALSE}

@@

+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Name                                            | Authors | Translations | Description                                                                            | Relevant Items |
+=================================================+=========+==============+========================================================================================+================+
| Visual Light Sensitivity Questionnaire-8        |         |              | Eight-question survey to assess the presence and severity of photosensitivity symptoms |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Office Light Survey                             |         |              | To assess electrical lighting environment in Office                                    |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Harvard Light Exposure Assessment Questionnaire |         |              | Self-administered semiquantitative light questionnaire                                 |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Hospital Lighting Survey                        |         |              | 23 items questionnaire to assess light environment in a hospital                       |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Morningness-Eveningness Questionnaire           |         |              | 19 items questionnaire to understand your body clock                                   |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Munich Chronotype Questionnaire (MCTQ)          |         |              | 17 items questionnaire to understand individuals phase of entrainment                  |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| Assessment of Sleep Environment                 |         |              | 13 items questionnaire measuring your sleep environment quality                        |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
| The Pittsburgh Sleep Quality Index (PSQI)       |         |              | 9 items inventory to measure sleep quality and sleeping pattern                        |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
|                                                 |         |              |                                                                                        |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
|                                                 |         |              |                                                                                        |                |
+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+

: Existing related Scales

@@

```{r Parallel, include=FALSE}

@@

```{r ScreePlot, include=FALSE}
Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
      hline=NULL,add=F)

@@

```{r Hull, include=FALSE}
# HULL
hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
        details = TRUE)
hull <- ggplot2::last_plot()
Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ theme(panel.grid.major = element_blank(),
                                               panel.grid.minor = element_blank(),
                                               panel.background = element_blank(),
                                               axis.line.x = element_line(color='black'),
                                               axis.line.y = element_line(color='black'))

@@

```{r MAP, include=FALSE}
#MAP
psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
```
